---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


wd = setwd("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination")
library(tseriesChaos);library(nonlinearTseries);library(SparseM);library(crqa);library(lme4);library(modelr);library(tibble);library(MuMIn);library(stringr);library(dplyr);library(caret);library(Metrics);library(pROC);library(groupdata2);library(ggplot2); library(dplyr); library(gridExtra);library(stringr)

```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.


2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.



3) Do you observe differences in coordination between conditions? Report the models and results.



4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?
- Run crqa on heart rate and respiration data (find parameters, run crqa)

```{r}
#exploring


#Choosing pair 8
#Load data
Turntake = read.csv("Study2_G8_T1_TurnTaking.csv")
Synch =read.csv("Study2_G8_T2_Synchronous.csv")
Conversation = read.csv("Study2_G8_T3_Conversation.csv")



#downsampling
Turntake = Turntake %>%
  group(n = 100, method = 'greedy') %>%    
  dplyr::summarise(time = mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T),HR2 = mean(HR2,na.rm=T), Resp1 = mean(Resp1,na.rm=T), Resp2 = mean(Resp2,na.rm=T))

Synch = Synch %>%
  group(n = 100, method = 'greedy') %>%    
  dplyr::summarise(time = mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T),HR2 = mean(HR2,na.rm=T), Resp1 = mean(Resp1,na.rm=T), Resp2 = mean(Resp2,na.rm=T))

Conversation = Conversation %>%
  group(n = 100, method = 'greedy') %>%    
  dplyr::summarise(time = mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T),HR2 = mean(HR2,na.rm=T), Resp1 = mean(Resp1,na.rm=T), Resp2 = mean(Resp2,na.rm=T))


#plots
#turntaking
Resp_turn = ggplot(Turntake, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue") + labs(title = "Resp_turn")
HR_turn = ggplot(Turntake, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue") + labs(title = "HR_turn")

#synch
Resp_synch = ggplot(Synch, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Synch") + labs(title = "Resp_synch")
HR_synch = ggplot(Synch, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")+ labs(title = "HR_synch")

#Conversation
Resp_Conv = ggplot(Conversation, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Conv")
HR_Conv = ggplot(Conversation, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")

#put together in one grid
Gridplot = grid.arrange(Resp_turn,Resp_synch, Resp_Conv, HR_turn, HR_synch, HR_Conv, ncol=3)


#Outlier removal function:

#set threshold for outlier removal
threshold= 2.5

removeOuts = function(ts,threshold)
{
  ts[ts > (mean(ts,na.rm=TRUE)+(threshold*sd(ts,na.rm=TRUE)))|
       ts < (mean(ts,na.rm=TRUE)-(threshold*sd(ts,na.rm=TRUE)))] = mean(ts,na.rm=TRUE) 
  return(ts)
  }

#remove artifacts
Turntake$HR1 = removeOuts(Turntake$HR1, threshold)
Turntake$HR2 = removeOuts(Turntake$HR2, threshold)
Turntake$Resp1 = removeOuts(Turntake$Resp1, threshold)
Turntake$Resp2 = removeOuts(Turntake$Resp2, threshold)

Synch$HR1 = removeOuts(Synch$HR1, threshold)
Synch$HR2 = removeOuts(Synch$HR2, threshold)
Synch$Resp1 = removeOuts(Synch$Resp1, threshold)
Synch$Resp2 = removeOuts(Synch$Resp2, threshold)

Conversation$HR1 = removeOuts(Conversation$HR1, threshold)
Conversation$HR2 = removeOuts(Conversation$HR2, threshold)
Conversation$Resp1 = removeOuts(Conversation$Resp1, threshold)
Conversation$Resp2 = removeOuts(Conversation$Resp2, threshold)

#Scale = - mean/sd
Turntake$HR1 = scale(Turntake$HR1)
Turntake$HR2 = scale(Turntake$HR2)
Turntake$Resp1 = scale(Turntake$Resp1)
Turntake$Resp2 = scale(Turntake$Resp2)

Synch$HR1 = scale(Synch$HR1, threshold)
Synch$HR2 = scale(Synch$HR2, threshold)
Synch$Resp1 = scale(Synch$Resp1, threshold)
Synch$Resp2 = scale(Synch$Resp2, threshold)

Conversation$HR1 = scale(Conversation$HR1)
Conversation$HR2 = scale(Conversation$HR2)
Conversation$Resp1 = scale(Conversation$Resp1)
Conversation$Resp2 = scale(Conversation$Resp2)








#plots for group 4, 5 6 
#Load data


Turntake4 = read_csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study1_G4_T3_TurnTaking.csv")
Synch4 =read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study1_G4_T1_Synchronous.csv")

Turntake5 = read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G5_T2_TurnTaking.csv")
Synch5 =read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G5_T1_Synchronous.csv")
Conversation5 = read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G5_T3_Conversation.csv")

Turntake6 = read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G6_T1_TurnTaking.csv")
Synch6 =read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G6_T3_Synchronous.csv")
Conversation6 = read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G6_T2_Conversation.csv")


Turntake9 = read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G9_T3_TurnTaking.csv")
Synch9 =read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G9_T1_Synchronous.csv")
Conversation9 = read.csv("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination/Preproc_data/Study2_G9_T2_Conversation.csv")


#group 9 



#plots

#Group 4

#turntaking
Resp_turn4 = ggplot(Turntake4, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue") + labs(title = "Resp_turn")
HR_turn4 = ggplot(Turntake4, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue") + labs(title = "HR_turn")

#synch
Resp_synch4 = ggplot(Synch4, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Synch") + labs(title = "Resp_synch")
HR_synch4 = ggplot(Synch4, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")+ labs(title = "HR_synch")


#group5

#turntake
Resp_turn5 = ggplot(Turntake5, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue") + labs(title = "Resp_turn")
HR_turn5 = ggplot(Turntake5, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue") + labs(title = "HR_turn")

#synch
Resp_synch5 = ggplot(Synch5, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Synch") + labs(title = "Resp_synch")
HR_synch5 = ggplot(Synch5, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")+ labs(title = "HR_synch")

#Conversation
Resp_Conv5 = ggplot(Conversation5, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Conv")
HR_Conv5 = ggplot(Conversation5, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")


#group6

#turntake
Resp_turn6 = ggplot(Turntake6, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue") + labs(title = "Resp_turn")
HR_turn6 = ggplot(Turntake6, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue") + labs(title = "HR_turn")

#synch
Resp_synch6 = ggplot(Synch6, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Synch") + labs(title = "Resp_synch")
HR_synch6 = ggplot(Synch6, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")+ labs(title = "HR_synch")

#Conversation
Resp_Conv6 = ggplot(Conversation6, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Conv")
HR_Conv6 = ggplot(Conversation6, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")

#group9

#turntake
Resp_turn9 = ggplot(Turntake9, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue") + labs(title = "Resp_turn")
HR_turn9 = ggplot(Turntake9, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue") + labs(title = "HR_turn")

#synch
Resp_synch9 = ggplot(Synch9, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Synch") + labs(title = "Resp_synch")
HR_synch9 = ggplot(Synch9, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")+ labs(title = "HR_synch")

#Conversation
Resp_Conv9 = ggplot(Conversation9, aes(time, Resp1)) + geom_line()+ geom_line(aes(time, Resp2), colour = "Blue")+ labs(title = "Resp_Conv")
HR_Conv9 = ggplot(Conversation9, aes(time, HR1)) + geom_line()+ geom_line(aes(time, HR2), colour = "Blue")+ labs(title = "HR_turn")

#put together in one grid
Gridplot4 = grid.arrange(Resp_turn4,Resp_synch4, HR_turn4, HR_synch4, ncol=3)

Gridplot5 = grid.arrange(Resp_turn5,Resp_synch5, Resp_Conv5, HR_turn5, HR_synch5, HR_Conv5, ncol=3)

Gridplot6 = grid.arrange(Resp_turn6,Resp_synch6, Resp_Conv6, HR_turn6, HR_synch6, HR_Conv6, ncol=3)

Gridplot9 = grid.arrange(Resp_turn9,Resp_synch9, Resp_Conv9, HR_turn9, HR_synch9, HR_Conv9, ncol=3)


```

Preprocess all files
and make function for parametre selection


```{r}

#Preprocess for all files




files <- list.files(path = wd, pattern = "Study", recursive = FALSE)
files

length(files)

# make empty list for all the information of interest

study = NULL
group = NULL
trial = NULL
condition = NULL

threshold = 2.5 
  
#increase n by 1 to index into the next value in the lists
n = 1

for (i in files){
  
  df = read.csv(i)
  
  
  #downsampling
  df = df %>% group(n = 100, method = 'greedy') %>% dplyr::summarise(time = mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T),HR2 = mean(HR2,na.rm=T),Resp1 = mean(Resp1,na.rm=T),Resp2 = mean(Resp2,na.rm=T))
  
  
  
  #removing artefacts
  df$Resp1 <- removeOuts(df$Resp1,threshold)
  df$Resp2 <- removeOuts(df$Resp2,threshold)
  df$HR1 <- removeOuts(df$HR1,threshold)
  df$HR2 <- removeOuts(df$HR2,threshold)
  
  #scaling the data
  df$Resp1 <- scale(df$Resp1)
  df$Resp2 <- scale(df$Resp2)
  df$HR1 <- scale(df$HR1)
  df$HR2 <- scale(df$HR2)
  
#write preprocessed files in a new folder  
  setwd("Preproc_data/")
  write.csv(df,file = i)
  setwd("C:/Users/annaa/OneDrive/3. semester/Exp. Method 3/Practical/Assignment 4 - coordination")

}





#make function that finds parametres and crqa data


fitCrqa <- function(ts1,ts2){
  par = list(lgM = 30, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 100, normalize = 0, rescale = 0,
             mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")

  Pars = try(optimizeParam(ts1, ts2, par, min.rec = 2, max.rec = 8))

  if (length(Pars)>1){
    Results=crqa(ts1, ts2, delay=Pars$delay, embed=Pars$emddim, radius=Pars$radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)
    } else {
      Results=NULL
      Pars=NULL
      Pars$delay=NA
      Pars$emddim=NA
      Pars$radius=NA
      Results$RR=NA
      Results$DET=NA
      Results$maxL=NA
      Results$L=NA
      Results$ENTR=NA
      Results$LAM=NA
      Results$TT=NA
}

df=data.frame(Delay=Pars$delay,Embed=Pars$emddim,Radius=Pars$radius,RR=Results$RR,DET=Results$DET,LMAX=Results$maxL,L=Results$L,ENTR=Results$ENTR,LAM=Results$LAM,TT=Results$TT)

return(df)

}





```

### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.
- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

```{r}

#run crqa on preprocessed data




setwd("Preproc_data/")
files_preproc = list.files(path=".")

final_df = NULL

study = NULL
group = NULL
trial = NULL
condition = NULL


n=1

for (i in files_preproc) {
  
  study[n] = substr(i,6,6)
  group[n] = substr(i,9,9)
  trial[n] = substr(i,12,12)
  condition[n] = substr(i,14,17)
  
  df = read.csv(i)
  results_resp = crqa (df$Resp1, conv$Resp2, delay=resp_delay, embed=resp_embed, radius=resp_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

  results_HR = crqa (df$HR1, conv$HR2, delay=HR_delay, embed=HR_embed, radius=HR_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)
  
  df <- data.frame(study = study[n], group = group[n], trial = trial[n], condition = condition[n], resp_RR = results_resp$RR, resp_DET = results_resp$DET, resp_NRLINE = results_resp$NRLINE, resp_maxL = results_resp$maxL, resp_L = results_resp$L, resp_ENTR = results_resp$ENTR, resp_rENTR = results_resp$rENTR, resp_LAM = results_resp$LAM, resp_TT = results_resp$TT, HR_RR = results_HR$RR, HR_DET = results_HR$DET, HR_NRLINE = results_HR$NRLINE, HR_maxL = results_HR$maxL, HR_L = results_HR$L, HR_ENTR = results_HR$ENTR, HR_rENTR = results_HR$rENTR, HR_LAM = results_HR$LAM, HR_TT = results_HR$TT)
  

  n = n + 1
}




```

### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs
 
 

```{r}


#Loop with shuffled files





setwd("/Preproc_data")
files_preproc = list.files(path=".")

shuffle_df = NULL

study = NULL
group = NULL
trial = NULL
condition = NULL

n = 1

for (i in files_preproc) {
  
  study[n] = substr(i,6,6)
  group_temp = str_extract(i, "G\\d+")
  group[n] = str_extract(group_temp, "\\d")
  trial_temp = str_extract(i, "T\\d")
  trial[n] = str_extract(trial_temp, "\\d")
  condition_temp = str_extract(i, c("Turn", "Conv", "Sync"))
  condition[n] = na.omit(condition_temp)
  
  df = read.csv(i)
  
  df$HR1 <- sample(df$HR1)
  df$HR2 <- sample(df$HR2)
  df$Resp1 <- sample(df$Resp1)
  df$Resp1 <- sample(df$Resp2)
  
  
  results_resp = crqa (df$Resp1, df$Resp2, delay=resp_delay, embed=resp_embed, radius=resp_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

  results_HR = crqa (df$HR1, df$HR2, delay=HR_delay, embed=HR_embed, radius=HR_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)
  
  df <- data.frame(study = study[n], group = group[n], trial = trial[n], condition = condition[n], resp_RR = results_resp$RR, resp_DET = results_resp$DET, resp_NRLINE = results_resp$NRLINE, resp_maxL = results_resp$maxL, resp_L = results_resp$L, resp_ENTR = results_resp$ENTR, resp_rENTR = results_resp$rENTR, resp_LAM = results_resp$LAM, resp_TT = results_resp$TT, HR_RR = results_HR$RR, HR_DET = results_HR$DET, HR_NRLINE = results_HR$NRLINE, HR_maxL = results_HR$maxL, HR_L = results_HR$L, HR_ENTR = results_HR$ENTR, HR_rENTR = results_HR$rENTR, HR_LAM = results_HR$LAM, HR_TT = results_HR$TT)
  
 if (exists("shuffle_df")) {
    shuffle_df = rbind(shuffle_df, df)
  } 
  else {
    shuffle_df = df
    
  n = n + 1
  }
}

write.csv(shuffle_df, file = "shuffle_df")




#testing differences between real and shuffled




#Testing effect of coordination on shuffled pairs 

 
final_df = read.csv("final_df (1)")
shuffle_df = read.csv("shuffle_df (1)")


#create a type of pair coloumn
shuffle_df$typePairs <- "shuffled" 
final_df$typePairs <- "real"

shuffle_final_df <- rbind(final_df, shuffle_df)

#model respiration coordination
model_resp_L <- lmerTest::lmer(resp_L~typePairs + trial + (1+trial|group), data = shuffle_final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

r.squaredGLMM(model_resp_L)
summary(model_resp_L)

#model heart rate coordination 
model_HR_L <- lmerTest::lmer(HR_L~typePairs + trial + (1+trial|group), data = shuffle_final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

summary(model_HR_L)
r.squaredGLMM(model_HR_L)




resp_box <- ggplot(shuffle_final_df, aes(shuffle_final_df$typePairs, shuffle_final_df$resp_L)) + geom_point() + geom_boxplot() + labs(title = "Respiration data") + labs(x = "Condition", y = "L - Respiration")

HR_box <- ggplot(shuffle_final_df, aes(shuffle_final_df$typePairs, shuffle_final_df$HR_L)) + geom_point() + geom_boxplot() + labs(title = "Heart rate data") + labs(x = "Condition", y = "L - Heart rate")

grid.arrange(resp_box,HR_box, ncol = 2)





 
```
 
### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs
 

```{r}

#create surrogate pairs 


#Loop with shuffled files

wd = setwd("/Preproc_data")
prepro_filelist = list.files(path=wd, pattern = "Study1") # load the preprocessed files

#Loop, surrogate study 1
prepro_filelist = list.files(path=wd, pattern = "Study1") # load the preprocessed files

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.

#!# temp info
#co = "Synchronous"
#i = 1
 
# Per each condition
for (co in c("Synchronous","TurnTaking")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study1_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study1_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2,Resp1S=d1$Resp1,Resp2S=d2$Resp2,HR1S=d1$HR1,HR2S=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2,Resp1S=d2$Resp1,Resp2S=d1$Resp2,HR1S=d2$HR1,HR2S=d1$HR2)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1,Resp1S=d1$Resp1,Resp2S=d2$Resp1,HR1S=d1$HR1,HR2S=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2,Resp1S=d2$Resp2,Resp2S=d1$Resp2,HR1S=d2$HR2,HR2S=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write.csv(d3,file.path("surrogate",file3))
  write.csv(d4,file.path("surrogate",file4))
  write.csv(d5,file.path("surrogate",file5))
  write.csv(d6,file.path("surrogate",file6))
  }
}

##NOW DO THE SAME FOR STUDY 2##







```

### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?
 
```{r}

#effects on condition

model_resp_L <- lmerTest::lmer(HR_L~condition + trial + (1+trial|group), data = final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

summary(model_resp_L)
r.squaredGLMM(model_resp_L)



model_HR_L <- lmerTest::lmer(HR_L~condition + trial + (1+trial|group), data = final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

summary(model_HR_L)
r.squaredGLMM(model_HR_L)



#plots

cond_resp = ggplot(final_df, aes(x = final_df$condition, y = final_df$resp_L)) + geom_point() + geom_boxplot()+ labs(title = "Respiration data") + labs(x = "Condition", y = "L - Respiration")


cond_HR = ggplot(final_df, aes(x = final_df$condition, y = final_df$HR_L)) + geom_point() + geom_boxplot()+labs(title = "Heart rate data") + labs(x = "Condition", y = "L - Heart rate")


grid.arrange(cond_resp,cond_HR, ncol = 2)

```

### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them
 
 
 
```{r}




m1 = lmerTest::lmer(HR ~ resp_L + (1|group), data = final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

summary(m1)

r.squaredGLMM(m1)
 
````